---
title: "Practical Statistics for Data Scientists (R) | Chapter 1. Exploratory Data Analysis"
output: html_notebook
---

> (c) 2019 Peter C. Bruce, Andrew Bruce, Peter Gedeck

I've started reading this book and am working on exercises for the book.

Start by importing several libraries.
Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 
```{r}
install.packages("dplyr")
```
```{r}
install.packages("tidyr")
install.packages("ggplot2")
install.packages("vioplot")
install.packages("corrplot")
install.packages("gmodels")
install.packages("matrixStats")

```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(vioplot)
library(corrplot)
library(gmodels)
library(matrixStats)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

